---
title: "7003 Final Project Step 2"
author: "Youngmin Choi"
date: "2023-11-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Objective/Goal
* To explore molecular changes at different stages of cancer in comparison to normal tissue.
* For this step (Step2), DEG list from Step 1 was used for enrichment analysis. 

## 2. Analysis Steps

### 1) Import Packages & File For EnrichR Analysis

```{r}
library(enrichR)
library(openxlsx)

dbs <- enrichR::listEnrichrDbs()

dblist <- read.csv(file='input/2023-EnrichR-Databases.txt', header=F, stringsAsFactors = F)
head(dblist)
```


### 2) Import T-Test Result (Filtered DEG list)

```{r}
sortedTTestResult <- read.csv('output/YoungminChoi_7003Final_DEGs_clean.csv')
head(sortedTTestResult)
```


### 3) Load Database & Call Function to Run Enrichment 

```{r}
geneListFinal <-sortedTTestResult$Feature

outputFilename <- 'output/YoungminChoi_7003Final_EnrichR.xlsx'
source(file='functionEnrichment.R')
functionEnrichment(dblist, geneListFinal, outputFilename)
```

## 3. Summary
* For Step 2, enrichment analysis was conducted.
* In the final output file, pathways from various database sources were included. 




